Compositional equivalences based on Open pNets

### 2021-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
petit topo Raffinement

>>>>

pNets have through composition  the ability both to add new holes to a system and to fill holes, obtaining a system with less holes. They support the refinement checking at the automata level through a simulation approach, with symbolic evaluation of
the guards and transitions. The definition of simulation on open automata should be  stronger than a strict simulation since it matches a transition with a family of transitions. Such a relation should be able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions, reinforcing guards, modifying variables. But it also should  support the  comparison of automata that do not have the same number of holes.
